---
title: "STA DressCode - SQA Qualifications"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    #vertical_layout: fill
    theme: bootstrap
    social: menu
 #   source_code: embed

---

```{css, echo = FALSE}

  .wide_image {
    overflow-x:scroll;
    white-space: nowrap;
  }

  .wide_image img {
    max-width: none;
  }

  .large_image {
    overflow:scroll;
    white-space: nowrap;
  }

  .show_hide_element_box {
    #color: #fff;
    /* padding: 20px; */
    display: none;
    /* margin-top: 20px; */
  }

```


```{r global-options, include = FALSE, cache = FALSE}

knitr::opts_chunk$set(out.width = '95%', fig.align = 'center',
                      echo = FALSE, warning = FALSE, message = FALSE)

# fig.dim = c(12, 5), out.height = '100%',
```

```{r libraries_and_utilities}

#library(tidyverse)
#library(ggtext)
#library(DBI)

#library(plotly)

library(knitr)
library(kableExtra)

# utilities & c.

knitr::read_chunk("base/sta_it_402_dc_interactive.r")

source("base/it-402-dc-data_initial_exploration-base.r")
source("base/common_interaction.r", local = knitr::knit_global())

# need to reduce font sizes here ...
dressCodeTheme <- dressCodeTheme +
        theme(plot.title = element_text(lineheight = 0.8, size = 11, colour = "grey50", face = "bold",
                                          margin = margin(t = 10, b = 10)),
              axis.text.y = element_text(size = 8), # element_markdown
              axis.text.x = element_text(size = 7.5, angle = 45, vjust = 0.5),
              axis.title = element_text(size = 10),
              legend.title = element_text(size = 9.5), legend.text = element_text(size = 8),
              strip.text = element_text(size = 10)
            )

```

```{r data_etl, cache = TRUE}

dbConn <- dbConnect(RSQLite::SQLite(), paste0(path_to_file_store, "/", "sqa-data-db.sqlite"))
#dbConn

source("base/sta_it_402_dc_data_etl.r", local = knitr::knit_global())
source("base/sta_it_402_dc_data_parsing.r", local = knitr::knit_global())

r_dataframe_to_js(sqa_qualifications_ordering$qualification, var_name = "qualifications")
r_dataframe_to_js(sqa_qualifications_ordering$qualification_label, var_name = "qualification_labels")

```


```{js, echo = FALSE}
/*  adapted from https://khaalipaper.com/javascript/show-hide-div-based-on-dropdown-selection-in-jquery.php#parentHorizontalTab1 */


$("#qualification_selector_cf_english_maths").ready(function() {
  createSelector("cf_english_maths", "sqa_qualification_plot_cf_english_maths_");
});

$("#qualification_selector_cf_sciences").ready(function() {
  createSelector("cf_sciences", "sqa_qualification_plot_cf_sciences_");
});


$("#plot_options_cf_english_maths").ready(function() {
  $("#plot_options_cf_english_maths").change(function() {

    $(this).find("option:selected").each(function() {
      var optionValue = $(this).attr("value");

      if (optionValue) {

        var qualification = optionValue.substring(optionValue.lastIndexOf("_") + 1)
        optionValue = optionValue.substr(0, optionValue.lastIndexOf("_") + 1) +
                          (qualifications.indexOf(qualification) + 1)
        console.log(qualification)
        console.log(optionValue)

        $(".show_hide_element_box").not("." + optionValue).hide();
        $("." + optionValue).show();
        window.scrollTo(0, 10000);

      } else {
        $(".show_hide_element_box").hide();
      }

    });
  }).change();
});

$("#plot_options_cf_sciences").ready(function() {
  $("#plot_options_cf_sciences").change(function() {

    $(this).find("option:selected").each(function() {
      var optionValue = $(this).attr("value");

      if (optionValue) {

        var qualification = optionValue.substring(optionValue.lastIndexOf("_") + 1)
        optionValue = optionValue.substr(0, optionValue.lastIndexOf("_") + 1) +
                          (qualifications.indexOf(qualification) + 1)
        console.log(qualification)
        console.log(optionValue)

        $(".show_hide_element_box").not("." + optionValue).hide();
        $("." + optionValue).show();
        window.scrollTo(0, 10000);

      } else {
        $(".show_hide_element_box").hide();
      }

    });
  }).change();
});


function createSelector(selector_id, id_prefix) {
  var qualificationSelector = document.createElement("select");
  qualificationSelector.setAttribute("id", ("plot_options_" + selector_id));
  document.getElementById("qualification_selector_" + selector_id).appendChild(qualificationSelector);

  var qualification = document.createElement("option");
  qualification.appendChild(document.createTextNode("Select Qualification"));
  qualificationSelector.appendChild(qualification);

  qualifications.forEach(createOptionElements);


  function createOptionElements(item, index) {

    var qualification = document.createElement("option");
    qualification.setAttribute("value", id_prefix + item);
    qualification.appendChild(document.createTextNode(qualification_labels[index]));

    qualificationSelector.appendChild(qualification);
  }
}

```


Sidebar {.sidebar}
=======================================================================

## TBC




Overview
=======================================================================

> SQA ...


## When is Computing Offered?

```{r, computing_offering_across_qualifications, fig.height = 3}
```


Gender Distribution {data-navmenu="Exploring the Data&nbsp;&ndash;&nbsp;Pupils"}
=======================================================================

Row {data-height=100}
-----------------------------------------------------------------------

> Change over time &ndash; __gender distribution__ uptake across all subjects and qualifications, compared to gender distribution for computing subjects only.
<!-- (Mouse over the edge of each line for percentages.) -->

Column
-----------------------------------------------------------------------

### Pupil Uptake &ndash; All Subjects {data-height=600}


```{r, gender_distribution_static_charts_overall }

```{r, gender_distribution_overall, fig.height = 6.5}

# gender_distribution_overall}
```

### Pupil Uptake &ndash; Computing {data-height=600}

```{r, gender_distribution_static_charts_computing }

```{r, gender_distribution_computing, fig.height = 6.5}

# gender_distribution_computing}
```

Column {data-height=150}
-----------------------------------------------------------------------

### Average gender distribution (across qualifications and over time)

```{r, summary_tables_gender_distribution_overall}
```

### Average gender distribution, computing only

```{r, summary_tables_gender_distribution_computing}
```


Subject Popularity {data-navmenu="Exploring the Data&nbsp;&ndash;&nbsp;Pupils"}
=======================================================================


Row {.tabset .tabset-fade}
-----------------------------------------------------------------------

### Top 5 Subjects

> __Subject popularity__ varies by gender and over time, as well as qualification and level or stage. These charts show subjects that fell within the top five selected by pupils each year for each qualification (excluding English and Maths). Relatively larger points indicate higher popularity across all qualifications, and position on the horizontal axis popularity for a qualification for that year. For instance, a medium-sized circle on the far right shows high popularity for a particular qualification, but lower popularity in general, across all qualifications. Subject popularity overall is also ordered top to bottom.

```{=html}
<hr width = "85%" hlign = "center" />
<p><br /></p>

```

####

```{r, top_5_subjects_over_time}
```


### Computing Subjects

#### Gender Distribution across all Qualifications

```{r, computing_uptake_over_time}
```

####  Gender Distribution by Qualification

```{r, computing_uptake_over_time_by_qualification}
```


### Computing vs. English &amp; Maths

<div class="large_image">

#### Subject Takeup Overall

  ```{r, computing_uptake_over_time_cf_english_maths_summary}
  ```

#### Gender Distribution Overall

  ```{r, computing_uptake_over_time_cf_english_maths}
  ```

#### Gender Distribution by Qualification

  ```{=html}

  ```{r, computing_uptake_over_time_cf_english_maths_by_qualification}
  ```

  <div id = "qualification_selector_cf_english_maths">
  </div>
  <p>&nbsp;<br /></p>

  ```

  <div class="sqa_qualification_plot_cf_english_maths_1 show_hide_element_box"> `r plots_cf_english_maths[[1]] ` </div>
  <div class="sqa_qualification_plot_cf_english_maths_2 show_hide_element_box"> `r plots_cf_english_maths[[2]] ` </div>
  <div class="sqa_qualification_plot_cf_english_maths_3 show_hide_element_box"> `r plots_cf_english_maths[[3]] ` </div>
  <div class="sqa_qualification_plot_cf_english_maths_4 show_hide_element_box"> `r plots_cf_english_maths[[4]] ` </div>
  <div class="sqa_qualification_plot_cf_english_maths_5 show_hide_element_box"> `r plots_cf_english_maths[[5]] ` </div>
  <div class="sqa_qualification_plot_cf_english_maths_6 show_hide_element_box"> `r plots_cf_english_maths[[6]] ` </div>
  <div class="sqa_qualification_plot_cf_english_maths_7 show_hide_element_box"> `r plots_cf_english_maths[[7]] ` </div>
  <div class="sqa_qualification_plot_cf_english_maths_8 show_hide_element_box"> `r plots_cf_english_maths[[8]] ` </div>
  <div class="sqa_qualification_plot_cf_english_maths_9 show_hide_element_box"> `r plots_cf_english_maths[[9]] ` </div>
  <div class="sqa_qualification_plot_cf_english_maths_10 show_hide_element_box"> `r plots_cf_english_maths[[10]] ` </div>
  <div class="sqa_qualification_plot_cf_english_maths_11 show_hide_element_box"> `r plots_cf_english_maths[[11]] ` </div>
  <div class="sqa_qualification_plot_cf_english_maths_12 show_hide_element_box"> `r plots_cf_english_maths[[12]] ` </div>
  <div class="sqa_qualification_plot_cf_english_maths_13 show_hide_element_box"> `r plots_cf_english_maths[[13]] ` </div>
  <div class="sqa_qualification_plot_cf_english_maths_14 show_hide_element_box"> `r plots_cf_english_maths[[14]] ` </div>

</div>


### Computing vs. Science Subjects


<div class="large_image">

#### Subject Takeup Overall 

```{r, computing_uptake_over_time_cf_sciences_summary}
```


#### Gender Distribution

```{r, computing_uptake_over_time_cf_sciences}
```

#### Gender Distribution by Qualification

  ```{=html}

  ```{r, computing_uptake_over_time_cf_sciences_by_qualification}
  ```

  <div id = "qualification_selector_cf_sciences">
  </div>
  <p>&nbsp;<br /></p>

  ```

  <div class="sqa_qualification_plot_cf_sciences_1 show_hide_element_box"> `r plots_cf_sciences[[1]] ` </div>
  <div class="sqa_qualification_plot_cf_sciences_2 show_hide_element_box"> `r plots_cf_sciences[[2]] ` </div>
  <div class="sqa_qualification_plot_cf_sciences_3 show_hide_element_box"> `r plots_cf_sciences[[3]] ` </div>
  <div class="sqa_qualification_plot_cf_sciences_4 show_hide_element_box"> `r plots_cf_sciences[[4]] ` </div>
  <div class="sqa_qualification_plot_cf_sciences_5 show_hide_element_box"> `r plots_cf_sciences[[5]] ` </div>
  <div class="sqa_qualification_plot_cf_sciences_6 show_hide_element_box"> `r plots_cf_sciences[[6]] ` </div>
  <div class="sqa_qualification_plot_cf_sciences_7 show_hide_element_box"> `r plots_cf_sciences[[7]] ` </div>
  <div class="sqa_qualification_plot_cf_sciences_8 show_hide_element_box"> `r plots_cf_sciences[[8]] ` </div>
  <div class="sqa_qualification_plot_cf_sciences_9 show_hide_element_box"> `r plots_cf_sciences[[9]] ` </div>
  <div class="sqa_qualification_plot_cf_sciences_10 show_hide_element_box"> `r plots_cf_sciences[[10]] ` </div>
  <div class="sqa_qualification_plot_cf_sciences_11 show_hide_element_box"> `r plots_cf_sciences[[11]] ` </div>
  <div class="sqa_qualification_plot_cf_sciences_12 show_hide_element_box"> `r plots_cf_sciences[[12]] ` </div>
  <div class="sqa_qualification_plot_cf_sciences_13 show_hide_element_box"> `r plots_cf_sciences[[13]] ` </div>
  <div class="sqa_qualification_plot_cf_sciences_14 show_hide_element_box"> `r plots_cf_sciences[[14]] ` </div>

</div>






Gender Distribution {data-navmenu="Exploring the Data&nbsp;&ndash;&nbsp;Teachers"}
=======================================================================

Row {data-height=60}
-----------------------------------------------------------------------

> Change over time &ndash; __gender distribution__ teacher FTE (full time equivalent) across all subjects, compared to gender distribution for computing subjects only.


Row {data-height=60}
-----------------------------------------------------------------------
```{=html}
<p>&nbsp;<br />

  <a href = "sta_it_402_dress_code_teacher_demographics.html" target = "_blank">Further detail on teacher demographics ...</a>
<!-- (Mouse over the edge of each line for percentages.) -->

```

Column
-----------------------------------------------------------------------

### Teacher FTE &ndash; All Subjects {data-height=600}


```{r, teacher_demographics_gender_distribution_fte_overall, fig.height = 3.2}

# gender_distribution_teacher_fte_overall}
```

### Teacher FTE &ndash; Computing as Main Subject {data-height=600}

```{r, teacher_demographics_gender_distribution_fte_computing, fig.height = 3.2}

# gender_distribution_teacher_fte_computing}
```

Column
-----------------------------------------------------------------------

### Average gender distribution over time

```{r, summary_tables_gender_distribution_teacher_fte_overall}
```

### Average gender distribution, computing only

```{r, summary_tables_gender_distribution_teacher_fte_computing}
```


```{r}
# cleanup ...

dbDisconnect(dbConn)
#dbConn

```
