---
title: "STA DressCode - Teacher Demographics"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
    theme: bootstrap
    social: menu
 #   source_code: embed

---

```{css, echo = FALSE}

  .wide_image {
    overflow-x:scroll;
    white-space: nowrap;
  }

  .wide_image img {
    max-width: none;
  }


  .medium_image {
    overflow-x:scroll;
    white-space: nowrap;
  }

  .medium_image img {
    max-width: 600px;
  }

  .large_image {
    overflow:scroll;
    white-space: nowrap;
  }

  .show_hide_element_box {
    #color: #fff;
    /* padding: 20px; */
    display: none;
    /* margin-top: 20px; */
  }

```


```{r global-options, include = FALSE, cache = FALSE}

knitr::opts_chunk$set(out.width = '95%', fig.align = 'center',
                      echo = FALSE, warning = FALSE, message = FALSE)

# fig.dim = c(12, 5), out.height = '100%',
```

```{r libraries_and_utilities}

#library(tidyverse)
#library(ggtext)
#library(DBI)

#library(RColorBrewer)
#library(plotly)

library(knitr)
library(kableExtra)

# utilities & c.

knitr::read_chunk("base/sta_it_402_dc_interactive.r")

source("base/it-402-dc-data_initial_exploration-base.r")
source("base/common_interaction.r", local = knitr::knit_global())

# need to reduce font sizes here ...
dressCodeTheme <- dressCodeTheme +
        theme(plot.title = element_text(lineheight = 0.8, size = 24, colour = "grey50", face = "bold",
                                          margin = margin(t = 10, b = 10)),
              axis.text.y = element_text(size = 14), # element_markdown
              axis.text.x = element_text(size = 16, angle = 45, vjust = 0.5),
              axis.title = element_text(size = 20),
              legend.title = element_text(size = 18), legend.text = element_text(size = 14),
              strip.text = element_text(size = 18)
            )

```

```{r data_etl, cache = TRUE}

dbConn <- dbConnect(RSQLite::SQLite(), paste0(path_to_file_store, "/", "sqa-data-db.sqlite"))
#dbConn

source("base/sta_it_402_dc_data_etl.r", local = knitr::knit_global())
source("base/teacher_demographics_etl.r", local = knitr::knit_global())
source("base/sta_it_402_dc_data_parsing.r", local = knitr::knit_global())

```


Overview
=======================================================================

### Change in Teacher Age over Time, Publicly Funded Schools in Scotland

```{r, teacher_demographics_head_count_teacher_age, fig.height = 5.8, fig.width = 18}
```


Teacher FTE &ndash; Computing {data-navmenu="Gender Distribution"}
=======================================================================


```{r, summary_cs_teacher_fte_main_subject_by_gender}
```


Row {data-height=280}
-------------------------------------

### Total Teacher FTE by Gender, Computing

```{r, teacher_fte_main_subject_by_gender_cs_total, fig.height = 5, fig.width = 8}
```

### Total Teacher FTE by Gender, Computing

```{r, teacher_fte_main_subject_by_gender_cs_total_zoomed_in, fig.height = 5, fig.width = 8}
```


Row {data-height=280}
-------------------------------------

### Teacher FTE by Gender, Computing as Main Subject

```{r, teacher_fte_main_subject_by_gender_cs_as_main, fig.height = 5, fig.width = 8}
```

### Teacher FTE by Gender, Computing as Main Subject

```{r, teacher_fte_main_subject_by_gender_cs_as_main_zoomed_in, fig.height = 5, fig.width = 8}
```


Row {data-height=280}
-------------------------------------

### Teacher FTE by Gender, Computing as Other Subject

```{r, teacher_fte_main_subject_by_gender_cs_as_other, fig.height = 5, fig.width = 8}
```

### Teacher FTE by Gender, Computing as Other Subject

```{r, teacher_fte_main_subject_by_gender_cs_as_other_zoomed_in, fig.height = 5, fig.width = 8}
```



```{r clean_up_summary_cs_teacher_fte_main_subject_by_gender }

rm(summary_cs_teacher_fte_main_subject_by_gender)

```



Teacher FTE &ndash; Computing cf. Sciences {data-navmenu="Gender Distribution"}
=======================================================================


```{r, summary_cs_sciences_teacher_fte_main_subject_by_gender}
```


Row {data-height=280}
-------------------------------------

### Total Teacher FTE by Gender, Sciences cf. Computing

```{r, summary_cs_sciences_teacher_fte_main_subject_by_gender_total, fig.height = 4.5, fig.width = 14}
```


Row {data-height=280}
-------------------------------------

### Teacher FTE by Gender, as Main Subject &ndash; Sciences cf. Computing

```{r, summary_cs_sciences_teacher_fte_main_subject_by_gender_as_main, fig.height = 4.5, fig.width = 14}
```


Row {data-height=280}
-------------------------------------

### Teacher FTE by Gender, as Other Subject &ndash; Sciences cf. Computing

```{r, summary_cs_sciences_teacher_fte_main_subject_by_gender_as_other, fig.height = 4.5, fig.width = 14}
```


Row {data-height=280}
-------------------------------------

### Teacher FTE by Gender, as Other Subject &ndash; Sciences (excl. General Science) cf. Computing

```{r, summary_cs_sciences_teacher_fte_main_subject_by_gender_as_other_excl_generaj_science, fig.height = 4.5, fig.width = 14}
```


```{r clean_up_summary_cs_sciences_teacher_fte_main_subject_by_gender }

rm(summary_cs_sciences_teacher_fte_main_subject_by_gender, focus_subject_group)

```



Teacher FTE {data-navmenu="Change in Age Distribution"}
=======================================================================

Column
-------------------------------------

### Teacher Age Ranges

<div class="medium_image">

```{r, teacher_demographics_age_fte_all_local_authorities, fig.height = 8, fig.width = 14}
```

```{r, teacher_demographics_age_median_fte_all_local_authorities, fig.height = 8, fig.width = 14}
```

</div>


### Teacher Age over Time

<div class="medium_image">

```{r, teacher_demographics_age_over_time_total_fte_all_local_authorities, fig.height = 8, fig.width = 14}
```

```{r, teacher_demographics_age_over_time_median_fte_all_local_authorities, fig.height = 8, fig.width = 14}
```

</div>



Teacher Headcount {data-navmenu="Change in Age Distribution"}
=======================================================================

Column
-------------------------------------


### Summary &ndash; Teacher Age over Time

```{r, teacher_demographics_head_count_teacher_age_statistics, fig.height = 8, fig.width = 14}
```


### Typical Teacher Age over Time

```{r, teacher_demographics_head_count_teacher_age_central_values, fig.height = 8, fig.width = 14}
```



Computing Compared to Selected Subjects I {data-navmenu="FTE&nbsp;&ndash;&nbsp;Subject Comparison"}
=======================================================================

Column
-------------------------------------

### Computing, English, Maths, Sciences (excl. General Science) & Modern Languages

```{r, teacher_demographics_age_fte_computing_cf_english_maths_sciences_modern_languages, fig.height = 8, fig.width = 14}
```


### Computing, Sciences (excl. General Science) & Modern Languages

```{r, teacher_demographics_age_fte_computing_cf_sciences_modern_languages, fig.height = 8, fig.width = 14}
```


Computing Compared to Selected Subjects II {data-navmenu="FTE&nbsp;&ndash;&nbsp;Subject Comparison"}
=======================================================================

Column
-------------------------------------

### Computing, English, Maths, All Sciences (incl. General Science), Modern & Community Languages

```{r, teacher_demographics_age_fte_computing_cf_english_maths_all_sciences_modern_languages, fig.height = 8, fig.width = 14}
```


### Computing, All Sciences (incl. General Science), Modern & Community Languages

```{r, teacher_demographics_age_fte_computing_cf_all_sciences_modern_languages, fig.height = 8, fig.width = 14}
```



Computing Compared to Selected Subjects III {data-navmenu="FTE&nbsp;&ndash;&nbsp;Subject Comparison"}
=======================================================================

Column
-------------------------------------

### Computing compared to Sciences

```{r, teacher_demographics_age_fte_computing_cf_sciences, fig.height = 8, fig.width = 14, out.width = '65%'}
```


### Computing compared to Modern Languages

```{r, teacher_demographics_age_fte_computing_cf_modern_languages, fig.height = 8, fig.width = 14}
```



Age Distribution {data-navmenu="FTE&nbsp;&ndash;&nbsp;Subject Comparison"}
=======================================================================

Row {.tabset .tabset-fade}
-----------------------------------------------------------------------

### Teacher FTE Change 2011-2021 &ndash; Computing compared to Sciences

```{r, teacher_demographics_age_over_time_computing_vs_sciences, fig.height = 7, fig.width = 14}
```


### Teacher FTE Change 2011-2021 &ndash; Computing compared to Modern Languages

```{r, teacher_demographics_age_over_time_computing_vs_modern_languages, fig.height = 7, fig.width = 14}
```



Age Distribution over Time {data-navmenu="FTE&nbsp;&ndash;&nbsp;Subject Comparison"}
=======================================================================

Row {.tabset .tabset-fade}
-----------------------------------------------------------------------

### Teacher FTE Change 2011-2021, by Age Range &ndash; Computing compared to Sciences

```{r, teacher_demographics_age_change_over_time_computing_vs_sciences, fig.height = 7, fig.width = 14}
```


### Teacher FTE Change 2011-2021, by Age Range &ndash; Computing compared to Modern Languages

```{r, teacher_demographics_age_change_over_time_computing_vs_modern_languages, fig.height = 7, fig.width = 14}
```


About
=======================================================================


```{=html}
<p>&nbsp;<br />

<a href = "https://www.gov.scot/publications/teacher-census-supplementary-statistics" target = "_blank"> Teacher census data</a> was obtained from the Scottish Govt Open Data Portal.


```


```{r}
# cleanup ...

dbDisconnect(dbConn)
#dbConn

```
